How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-29 manuscript/draft_manuscript.Rmd
plos results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyr)
library(pander)
library(ggplot2)
library(ggpubr)
library(knitr)
library(flextable)
panderOptions('table.emphasize.rownames', FALSE)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('big.mark', ',')
panderOptions('table.emphasize.rownames', FALSE)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('big.mark', ',')
panderOptions('keep.line.breaks', TRUE)
panderOptions('table.alignment.default','left')

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyr)
library(pander)
library(ggplot2)
library(ggpubr)
library(knitr)
library(flextable)
library(tidytext)
panderOptions('table.emphasize.rownames', FALSE)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('big.mark', ',')
panderOptions('table.emphasize.rownames', FALSE)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('big.mark', ',')
panderOptions('keep.line.breaks', TRUE)
panderOptions('table.alignment.default','left')

@@

```{r}
load('plos.results.10topics.rda')

ftab.plos = matches %>%
  group_by(topic_id) %>% summarise(DOIs = n(),`Median word count` = median(words),Q1=quantile(words,.25),Q3=quantile(words,.75),.groups='drop')

flextable(ftab.plos)
